\Title

### 2015-11-01 manuscript.tex
Simpler bibtex keys and restructure methods intro

In potential field methods,
we must isolate the target anomalous density distribution prior to modeling and
inversion.
In our case, the target is the relief of the real Moho undulating around a
reference Moho.
We do this by removing all other effects from the gravity observations.
The first correction is to remove the
gravity\footnote{The term ``gravity'' refers the sum of the gravitational and
centripetal accelerations.}
of an ellipsoidal Earth (the Normal Earth or reference ellipsoid).
This is done using the closed-form solution presented in
\citet{li_ellipsoid_2001}.
\todo{Needs review}
The resulting quantity is known as the gravity disturbance,

\begin{equation}
    \delta(P) = g(P) - \gamma(P)
\end{equation}

\noindent in which $g(P)$ is the measured gravity at an observation point $P$
and $\gamma(P)$ is the gravity of the Normal Earth
calculated at point $P$.

We assume that the crust of our Normal Earth has a standard density of
$\rho_{crust} = 2670\ kg.m^{-3}$ and a depth to the Moho of $z_{ref}$.
The disturbance contains only the gravitational effects of density
distributions that are anomalous with respect to the Normal Earth.
This includes all masses above the surface of the ellipsoid (the topography),
the mass deficiency of the oceans,
the mass deficiency of sedimentary basins,
crustal sources (e.g., igneous intrusions, lateral density changes, etc),
heterogeneities below the upper mantle,
and
the effect of the difference between the real Moho
topography and the reference Moho ($z_{ref}$).
In order to invert for the Moho topography, all effects must either be removed
or assumed negligible.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/paper/tesseroid-coord-sys}
    \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
        system (X, Y, Z).
        Observations are made at point P with respect to it's local
        North-oriented coordinate system (x, y, z).
        After \citet{uieda_tesserioid_2015},
        available at
        \url{http://dx.doi.org/10.6084/m9.figshare.1495525}.
    }
    \label{fig:tess}
\end{figure}

We parameterize the forward problem by discretizing the Moho undulation
into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids (Fig.~\ref{fig:tess}).
\todo{Cite source separation figure}
In cases where the Moho is above the reference depth ($z_{ref}$),
the top of the tesseroid is the Moho depth at the location of the $k$-eth
tesseroid ($z_{k}$),
the bottom is $z_{ref}$, and the density-contrast is positive.
If the Moho is below the $z_{ref}$, the top of the tesseroid is $z_{ref}$,
the bottom is the Moho depth, and the density-contrast is negative.

@@

\noindent in which $d_i$ is the $i$th element of the $N$-dimensional predicted
data vector $\mathbf{d}$, $\mathbf{p}$ is the $M$-dimensional parameter vector
containing the Moho depths ($z_k$),
and $f_i$ is the $i$th non-linear function that maps the parameters onto the
data.
$f_i$ is the radial component of the gravitational attraction of the tesseroid
model.
The gravitational attraction of a tesseroid is calculated using the
Gauss-Legendre Quadrature (GLQ) integration.
The accuracy of the GLQ integration is improved by an adaptive discretization
scheme.
\todo{Cite tesseroids paper.}

@@

\noindent
Thus, it does not require the computation and storage of the Hessian matrix
nor the solution of linear systems.
However, the Steepest Descent method has poor convergence when the
current solution is close to the minimum of the goal function
\citep{kelley_iterative_1987}.

@@

Non-linear inversions for the relief of an interface (like
the Moho) are ill-posed and required additional constraints in the form of
regularization \citep{silva_potential-field_2001}.
A common approach is to use the first-order Tikhonov regularization to impose
smoothness on the solution,

@@

\citet{bott_use_1960} developed an efficient method to determined the basement
relief of a sedimentary basin from gravity observations.
The method requires data on a regular grid of $N_x \times N_y = N$
observations.
The basement relief is then discretized into an equal grid of $M_x \times
M_y = M$ elements with $M_x = N_x$ and $M_y = N_y$.
Bott's iterative method starts with an initial estimate of the basement relief
$\mathbf{p}^0$ equal to the null vector and updates the estimate using the formula

@@

\citet{silva_fast_2014} showed that Bott's method can be formulated as
a special case of the Gauss-Newton method (Eq.~\ref{eq:gaussnewton})
by setting the Jacobian matrix (Eq.~\ref{eq:jacobian}) to

@@

A disadvantage of Bott's method is that it suffers from instability
\citep{silva_fast_2014}.
A common approach to solve this issue is to apply a smoothing filter, like a
moving average, to the unstable estimate.

@@

The gravitational effect of the topography
is removed using the
ETOPO1\footnote{\url{http://dx.doi.org/10.7289/V5C8276M}}
digital terrain model
\citep{amante_c._and_b._w._eakins_etopo1_2009}.
The effect of sedimentary basins is removed using the
CRUST1.0\footnote{\url{http://igppweb.ucsd.edu/~gabi/rem.html}} model
by
\citet{laske_update_2013}.
Lateral variations in density along the Moho cannot be properly accounted for
in regions where information coverage is sparse and readily accessible models
are not available, like in the South American and African continents.
For the purposes of this study, we will assume that all other crustal sources
and lateral variations in density are negligible.

>>>>

In potential field methods,
we must isolate the target anomalous density distribution prior to modeling and
inversion.
In our case, the target is the relief of the real Moho undulating around a
reference Moho.
We do this by removing all other effects from the gravity observations.
The first correction is to remove the
scalar gravity of an ellipsoidal reference Earth (the Normal Earth),
hereafter denoted as $\gamma$.
This effect is calculated on the same point $P$ where the observation was made
using the closed-form solution presented by \citet{li_2001}.
The difference between the observed gravity ($g$) and Normal gravity
is known as the gravity disturbance,

\begin{equation}
    \delta(P) = g(P) - \gamma(P).
\end{equation}

The disturbance contains only the gravitational effects of density
distributions that are anomalous with respect to the Normal Earth.
This includes all masses above the surface of the ellipsoid (the topography),
the mass deficiency of the oceans,
the mass deficiency of sedimentary basins,
crustal sources (e.g., igneous intrusions, lateral density changes, etc),
heterogeneities below the upper mantle,
and the effect of the difference between the real Moho
topography and the Moho of the Normal Earth.

All effects must either be removed or assumed negligible
to invert for the anomalous Moho.
The gravitational attraction of the topography, oceans, and basins are
calculated in a spherical Earth approximation by forward modeling using
tesseroids
(Fig.~\ref{fig:tesseroid}).
The tesseroid effects are calculated numerically using
Gauss-Legendre Quadrature (GLQ) integration \citep{asgharzadeh_2007}.
The accuracy of the GLQ integration is improved by the adaptive discretization
scheme of \citet{uieda_2016}.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/paper/tesseroid-coord-sys}
    \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
        system (X, Y, Z).
        Observations are made at point P with respect to it's local
        North-oriented coordinate system (x, y, z).
        After \citet{uieda_2015},
        available at
        \url{http://dx.doi.org/10.6084/m9.figshare.1495525}.
    }
    \label{fig:tesseroid}
\end{figure}

We parameterize the forward problem by discretizing the Moho undulation
into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids
(Fig.~\ref{fig:tesseroid}).
In cases where the Moho is above the reference depth ($z_{ref}$),
the top of the tesseroid is the Moho depth at the location of the $k$-eth
tesseroid ($z_{k}$),
the bottom is $z_{ref}$, and the density-contrast is positive.
If the Moho is below the $z_{ref}$, the top of the tesseroid is $z_{ref}$,
the bottom is the Moho depth, and the density-contrast is negative.

@@

\noindent in which $d_i$ is the $i$th element of the $N$-dimensional predicted
data vector $\mathbf{d}$, $\mathbf{p}$ is the $M$-dimensional parameter vector
containing the Moho depths ($z_k$),
and $f_i$ is the $i$th non-linear function that maps the parameters onto the
data.
$f_i$ is the radial component of the gravitational attraction of the tesseroid
model of the anomalous Moho.

@@

\noindent
Thus, it does not require the computation and storage of the Hessian matrix
nor the solution of linear systems.
However, the Steepest Descent method has poor convergence when the
current solution is close to the minimum of the goal function
\citep{kelley_1987}.

@@

Non-linear inversions for the relief of an interface (like
the Moho) are ill-posed and required additional constraints in the form of
regularization \citep{silva_2001}.
A common approach is to use the first-order Tikhonov regularization to impose
smoothness on the solution,

@@

\citet{bott_1960} developed an efficient method to determined the basement
relief of a sedimentary basin from gravity observations.
The method requires data on a regular grid of $N_x \times N_y = N$
observations.
The basement relief is then discretized into an equal grid of $M_x \times
M_y = M$ elements with $M_x = N_x$ and $M_y = N_y$.
Bott's iterative method starts with an initial estimate of the basement relief
$\mathbf{p}^0$ equal to the null vector and updates the estimate using the formula

@@

\citet{silva_2014} showed that Bott's method can be formulated as
a special case of the Gauss-Newton method (Eq.~\ref{eq:gaussnewton})
by setting the Jacobian matrix (Eq.~\ref{eq:jacobian}) to

@@

A disadvantage of Bott's method is that it suffers from instability
\citep{silva_2014}.
A common approach to solve this issue is to apply a smoothing filter, like a
moving average, to the unstable estimate.

@@

The gravitational effect of the topography
is removed using the
ETOPO1\footnote{\url{http://dx.doi.org/10.7289/V5C8276M}}
digital terrain model
\citep{amante_2009}.
The effect of sedimentary basins is removed using the
CRUST1.0\footnote{\url{http://igppweb.ucsd.edu/~gabi/rem.html}} model
by
\citet{laske_2013}.
Lateral variations in density along the Moho cannot be properly accounted for
in regions where information coverage is sparse and readily accessible models
are not available, like in the South American and African continents.
For the purposes of this study, we will assume that all other crustal sources
and lateral variations in density are negligible.
